---
title: "PS 811 Exercise 4"
author: "Mingcong Pan"
date: "10/22/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Base R tasks

* Load the CSV file into your R environment.
```{r}
data <- read.csv("food_coded.csv")
```

* Extract the first 95 rows.
```{r}
subdata <- data [1:95,]
```

* Look at the following variables using both name and column index/number.
  + GPA
  + calories_chicken
  + drink
  + fav_cuisine
  + father_profession
  + mother_profession
```{r eval=FALSE, results = FALSE, message=FALSE}
data$GPA
data$calories_chicken
data$drink
data$fav_cuisine
data$father_profession
data$mother_profession

data[,1] #GPA
data[,4] #calories_chicken
data[,16] #drink
data[,26] #fav_cuisine
data[,25] #father_profession
data[,45] #mother_profession
```

* Create a new variable for how healthy each person feels but convert the scale from 1 to 10 to 1 to 100.

```{r}
data$new_healthy_feeling <- data$healthy_feeling*10
```

* Filter to students who are female and have GPAs that are above 3.0.

```{r}
data.new <- data[data$GPA > 3, ]
```

* Find the mean and standard deviation for the following variables, and summarize them in a data frame.
  + chicken_calories
  + tortilla_calories
  + turkey_calories
  + waffle_calories
  
```{r}
data$calories_chicken <- as.numeric(data$calories_chicken)
data$tortilla_calories <- as.numeric(data$tortilla_calories)
data$turkey_calories <- as.numeric(data$turkey_calories)
data$waffle_calories <- as.numeric(data$waffle_calories)

variable <- c('chicken_calories', 'tortilla_calories', 'turkey_calories', 'waffle_calories')
mean <- c(mean(data$calories_chicken, na.rm = TRUE),mean(data$tortilla_calories, na.rm = TRUE),
          mean(data$turkey_calories, na.rm = TRUE),mean(data$waffle_calories, na.rm = TRUE))
sd <- c(sd(data$calories_chicken, na.rm = TRUE),sd(data$tortilla_calories, na.rm = TRUE),
        sd(data$turkey_calories, na.rm = TRUE),sd(data$waffle_calories, na.rm = TRUE))
df <- data.frame(variable, mean, sd)
df
```

* Summarize GPA and weight within the gender and cuisine variables.

```{r}
data$GPA <- as.numeric(data$calories_chicken)
data$weight <- as.numeric(data$tortilla_calories)

mean(data$GPA[data$Gender==1 & data$cuisine==1], na.rm = TRUE)
mean(data$GPA[data$Gender==1 & data$cuisine==2], na.rm = TRUE)
mean(data$GPA[data$Gender==1 & data$cuisine==3], na.rm = TRUE)
mean(data$GPA[data$Gender==1 & data$cuisine==4], na.rm = TRUE)
mean(data$GPA[data$Gender==1 & data$cuisine==5], na.rm = TRUE)
mean(data$GPA[data$Gender==1 & data$cuisine==6], na.rm = TRUE)
mean(data$GPA[data$Gender==2 & data$cuisine==1], na.rm = TRUE)
mean(data$GPA[data$Gender==2 & data$cuisine==2], na.rm = TRUE)
mean(data$GPA[data$Gender==2 & data$cuisine==3], na.rm = TRUE)
mean(data$GPA[data$Gender==2 & data$cuisine==4], na.rm = TRUE)
mean(data$GPA[data$Gender==2 & data$cuisine==5], na.rm = TRUE)
mean(data$GPA[data$Gender==2 & data$cuisine==6], na.rm = TRUE)

mean(data$weight[data$Gender==1 & data$cuisine==1], na.rm = TRUE)
mean(data$weight[data$Gender==1 & data$cuisine==2], na.rm = TRUE)
mean(data$weight[data$Gender==1 & data$cuisine==3], na.rm = TRUE)
mean(data$weight[data$Gender==1 & data$cuisine==4], na.rm = TRUE)
mean(data$weight[data$Gender==1 & data$cuisine==5], na.rm = TRUE)
mean(data$weight[data$Gender==1 & data$cuisine==6], na.rm = TRUE)
mean(data$weight[data$Gender==2 & data$cuisine==1], na.rm = TRUE)
mean(data$weight[data$Gender==2 & data$cuisine==2], na.rm = TRUE)
mean(data$weight[data$Gender==2 & data$cuisine==3], na.rm = TRUE)
mean(data$weight[data$Gender==2 & data$cuisine==4], na.rm = TRUE)
mean(data$weight[data$Gender==2 & data$cuisine==5], na.rm = TRUE)
mean(data$weight[data$Gender==2 & data$cuisine==6], na.rm = TRUE)
```

# Tidyverse tasks

* Load the CSV file into your R environment.

```{r}
data2 <- read.csv("facebook-fact-check.csv")
library(tidyverse)
```

* Extract the last 500 rows. (Mingcong's note: it seems the top_n() function extract top or bottom rows sorted by value. But here I using it as if it extract the original bottom 500 rows, instead of the sorted one)

```{r}
subdata2 <- data2 %>% top_n(-500)
```

* Look at the even-numbered column indices only. Identify them by name.

```{r message=FALSE, warning=FALSE}
names(data2)
test <- data2 %>% select("post_id","Page","Date.Published","Rating","share_count","comment_count")
```

* Using mutate, create a new variable called post_type_coded that renames each post type to the following:
  + link = 1
  + photo = 2
  + text = 3
  + video = 4

```{r results = FALSE, message=FALSE, warning=FALSE}
data2 %>% 
  mutate(post_type_coded = case_when(
    Post.Type == "link" ~ 1,
    Post.Type == "photo" ~ 2,
    Post.Type == "text" ~ 3,
    Post.Type == "video" ~ 4)) 
```

* Arrange page names in reverse order.

```{r results = FALSE, message=FALSE, warning=FALSE}
data2 %>% arrange(desc(Page))
```

* Find the mean and standard deviation for the following variables, and summarize them.
  + share_count
  + reaction_count
  + comment_count
  
```{r results = FALSE, message=FALSE, warning=FALSE}
data2 %>% 
  summarize(mean_share_count = mean(share_count, na.rm = TRUE),   
            mean_sreaction_count= mean(reaction_count, na.rm = TRUE),
            mean_comment_count = mean(comment_count, na.rm = TRUE),          
            sd_share_count = sd(share_count, na.rm = TRUE),
            sd_reaction_count = sd(reaction_count, na.rm = TRUE),
            sd_comment_count = sd(comment_count, na.rm = TRUE))

```

* Summarize the mean and standard deviations in Question 7 with the “mainstream” values in the category variable.

```{r results = FALSE, message=FALSE, warning=FALSE}
data2 %>% 
  group_by(Category) %>% 
  summarize(mean_share_count = mean(share_count, na.rm = TRUE),   
            mean_sreaction_count= mean(reaction_count, na.rm = TRUE),
            mean_comment_count = mean(comment_count, na.rm = TRUE),          
            sd_share_count = sd(share_count, na.rm = TRUE),
            sd_reaction_count = sd(reaction_count, na.rm = TRUE),
            sd_comment_count = sd(comment_count, na.rm = TRUE))


```